---
title: "Testing the link between regulatory agencies’ independence and credibility: Evidence from a survey experiment with regulatory stakeholders"
author: '**Saar Alon-Barkat**, **Madalina Busuioc** [alphabetical order]'
date: " "
output:
  html_document:
    theme: journal
    toc: yes
    toc_float:
      collapsed: yes
      smooth_scroll: yes
      toc_depth: 3
  pdf_document:
    toc: yes
  word_document: default
bibliography: efsa.bib
csl: https://raw.githubusercontent.com/citation-style-language/styles/master/chicago-author-date.csl
urlcolor: blue
always_allow_html: yes
---

<br>

Draft, last edited at `r Sys.Date()`.


```{r silent-packages, echo = FALSE, eval = TRUE, message=FALSE, include = FALSE}
library(sjPlot)
library(tidyverse)
library(car)
library(reshape2)
library(viridis)
library(ggthemes)
library(corrr)
library(kableExtra)
library(dotwhisker)
library(sjmisc)
library(interflex)
library(effsize)
library(broom)
library(sjstats)
library(stargazer)
library(AER)
library(ggpubr)

```



```{r , include=FALSE, echo=FALSE,warning=FALSE,message=FALSE}
#data

source("G:/My Drive/University/R/EFSA/code/efsa_dm_01.R")#change to your directory path
#source("https://raw.githubusercontent.com/saaralonbarkat/eufood/master/code/efsa_dm_01.R?token=ACU7DGTSVSI2B2UFAE776CC5F3Q3M")


efsa_00.t1 <- efsa_00 %>% 
  drop_na(independence.polit.efsa) %>% 
  data.frame() %>% 
  mutate(approve.pesticide = ban.pesticide %>% Recode("0=1;1=0"))

```

```{r, echo=FALSE, warning=FALSE, message=F}
#Figures and tables
table.x = 0
figure.x = 0
```



<br>

# METHODOLOGY
We empirically examine these hypotheses in relation the European Food Safety Authority (EFSA). We conducted an experiment, embedded in a survey among external stakeholders of EFSA, as detailed below. The employment of an experimental design enables us to rigorously examine the causal effects of perceived independence and prior standpoints on regulatory credibility. At the same time, by surveying real stakeholders about actual regulatory outputs of the agency, we substantiate the study’s generalizability to real-world settings.

While experiments have been widely used by public administration scholars in recent years to explore the perceptions of citizens and political representatives about public sector agencies [@baekgaard2015conducting; @grimmelikhuijsen2017behavioral; @jilke2016generating; for a systematic review of experimental studies in public administration see: @li2017systematic], to the best of our knowledge, this is the first study to experimentally examine the factors that shape the perceptions of a broad array of stakeholders regarding agencies’ scientific regulatory outputs. In addition, this is the first study to manipulate agencies' perceived independence from political stakeholders. In the following section, we provide background on the empirical case. Thereafter, we describe the population of survey respondents and their selection and recruitment, the course of the survey and experimental procedures, and the operationalization of our main variables.


<br>

## *European Food Safety Authority (EFSA) and pesticides regulation*
We put the assumption to test in a crucial case -- the case of the European Food Safety Agency. EFSA is an independent, non-majoritarian agency, operating at the EU level, a separate institutional body from the EU institutions and the member states, with its own staff and budget. The agency is the product of a credibility crisis, part of the reform process of European food safety regulation, in response to a set of damaging food scandals in the late 1990s, linked to the politicization of regulatory policy. The agency’s creation in 2002 formally signaled the separation of scientific risk assessment, carried out by EFSA, from risk management, carried out by the European Commission. The separation of science from politics was seen as critical in order to rebuilt public confidence in the European regulatory food policy after the BSE and dioxin crises in particular [@vos2000reforming; @groenleer2009autonomy; @busuioc2013european]. 

In light of the circumstances surrounding its creation, EFSA’s set up is strongly predicated on its independence from politics and this logic is heavily reflected in the agency’s structures: “There are few EU organisations that can claim as much formal autonomy as EFSA” [@groenleer2009autonomy, 181]. In contrast to other EU agencies, where management boards are overwhelmingly made up of national representatives (one representative for each member state), EFSA’s 15-member governing board is exceptionally appointed *in a personal capacity*. Moreover, to further ensure separation from political considerations, EFSA’s scientific committee and panel members are independent scientists that are not nominated by national authorities of the member states. Again, this is in contrast to other European agencies -- (e.g. the European Medicines Agency) where scientific committees contain members nominated by member states and the agency financially compensates national authorities for scientific work carried out for the EU agency [@groenleer2009autonomy].

EFSA’s mandate pertains to both risk assessment and risk communication and covers the areas of food and feed safety, nutrition, animal health and welfare, plant protection and plant health. In its risk assessor role, EFSA produces scientific opinions, which are adopted into biding decisions by the risk manager, the European Commission. The agency’s broad mandate covers areas that are heavily politicised in the European context such as the regulation of GMOs, pesticides or food additives. 

In light of the above, this renders it an especially relevant case to study the link between independence and credibility in contested environments. EFSA is a crucial case [@eckstein1975case; see also @gerring2016selecting], one that “must closely fit a theory if one is to have confidence in the theory’s validity” [@eckstein1975case], for the independence–credibility assumption. The pesticides case is especially relevant to study the impact of independence on perceptions of credibility. Pesticide regulation is a highly salient area, subject to much controversy with strong stances on (different sides of) the matter from the pesticide industry, green groups, farmers, organic industry and EU citizens at large. For instance in 2017, over 1,300,000 European citizens signed a petition to ban glyphosate, the world’s most widely-used herbicide, at the time up for regulatory assessment for the approval of its licence renewal. Following the controversy over glyphosate’s approval, EFSA’s executive director, Bernard Url, has publicly expressed his concern that advocacy organizations tend to judge EFSA’s scientific opinions selectively, depending on the extent to which scientific findings conform to their ideological stances: “We at EFSA believe that some campaigners are unwilling to accept any evidence that certain regulated substances are safe, and will tout weak scientific studies showing the opposite. The same groups applauded EFSA for reviews on other pesticides, such as neonicotinoids, that it deemed dangerous. It seems to us that some campaigners contest the science of safety assessments in pursuit of greater political arguments…" [@url2018don, 381]. Overall, over the years, EFSA has been criticized for its scientific opinions -- as not precautionary enough or as overly-precautionary -- by different pro and against ‘camps’ on a variety of regulatory issues and substances  [e.g. @groenleer2009autonomy; @rimkute2018organizational; @carrington2018eu; @carrington_website_2019].  

<br>

## *Data collection*

```{r, echo=FALSE, warning=FALSE, message=F}
n.invitations <- 654
n.errors <- 46
n.invitations_effective <- n.invitations-n.errors

n.start <- efsa_00 %>% nrow()
n.reach_credibility.pest <- efsa_00 %>% drop_na(credibility.pest.index) %>% nrow()
n.reach_independence <- efsa_00 %>% drop_na(independence.polit.efsa) %>% nrow()
n.reach_end <- efsa_raw %>% filter(Q13.13 !=0)%>% nrow()


n.reach_independence.recruited.directly <- efsa_00 %>%
                              drop_na(independence.polit.efsa) %>%
                              filter(recruited.directly==1) %>% 
                              nrow()

```

To build our sample of EFSA stakeholders, we constructed a list of names, organizational affiliation and contact details of potential stakeholders, based on a number of sources. First, we searched EFSA’s website and downloaded documents of EFSA meetings with stakeholders over the years, as well as a list of EFSA’s “registered stakeholders”. From these sources, we managed to extract the names of 392 persons from 259 organizations. These are what we would term “core stakeholders”— those participate in EFSA events and are registered as stakeholders with the agency. To broaden our sample, we then supplemented this list, with EU’s public *Transparency Register* data, which includes information on more than 10,000 organizations representing specific interests at EU level (available at: http://ec.europa.eu/transparencyregister). The register’s information is updated annually by the organizations themselves, and includes contact details of their “person with legal responsibility” and “person in charge of EU relations”. To restrict the list to stakeholders of EFSA, we filtered the dataset based on organizations’ self-reporting of their goals, activities and fields on interest. This search yielded a list of 3,155 persons from 2,045 different organizations related to the domains of ‘food and agriculture’, including representatives of the industry, NGOs and advocacy groups, professional organizations engaging in research, law firms and consultancy groups.[^footnote_construction_lists]

[^footnote_construction_lists]: All sources were downloaded on November 2018.   

For the list of participants in EFSA meetings and consultations (our “core” stakeholder group), we conducted both automatic and manual online searches, through which we managed to retrieve the emails of 229 stakeholders (`r ((229/392)*100) %>% round(0)`%). As for the broader stakeholder pool retrieved from the public transparency register, we conducted an automatic search to retrieve their email addresses by web-scrapping their organizations’ official websites, and matching the found email patterns with participants’ names and initials.[^footnote_email.scraping] Through this method, we retrieved the email addresses of additional 425 stakeholders.

[^footnote_email.scraping]: The codes will be available online at the project's website.

The survey was conducted online using the Qualtrics Survey software. Between February-May 2019, we sent a total of `r n.invitations` email invitations with anonymous links to the survey, followed by three reminders. We contacted stakeholders from a university email address, and invited the stakeholders to fill in the anonymous survey. We also asked them to invite other executives and staff members in their organizations to fill it out. Importantly, to avoid priming our respondents about food policy and mitigate potential selection bias, we did not directly inform them about the study’s focus on EFSA and food regulation. Rather, we generally presented it as an expert survey on EU regulatory policy, while noting that participants are asked about specific regulatory policy areas, which incidentally in their case is food safety.


```{r, echo=FALSE, warning=FALSE, message=F}
library(pwr)

pwr.80 <- pwr.t.test(power = 0.8,
           n=n.reach_independence/2,
           alternative = "greater",
           sig.level = 0.05)

pwr.d.35 <- pwr.t.test(#power = 0.8,
           n=n.reach_independence/2,
           d=0.35,
           alternative = "greater",
           sig.level = 0.05)

pwr.d.23 <- pwr.t.test(#power = 0.8,
           n=n.reach_independence/2,
           d=0.25,
           alternative = "greater",
           sig.level = 0.05)

```

Out of those contacted, `r n.start` people started filling the survey, and `r n.reach_independence` actually completed the main part (of which `r n.reach_independence.recruited.directly` were directly invited by us via email, and for the additional `r n.reach_independence - n.reach_independence.recruited.directly` the email invitation was forwarded by other respondents). This represents a sizable response rate of roughly `r (n.reach_independence.recruited.directly/n.invitations_effective*100)%>% round(0)`%.[^footnote_response.rate] Given the sample size, we estimate that a main effect of `r (pwr.80[["d"]] %>% round(2))` SDs for the experimental manipulations is detectible (power = 0.8).[^footnote_power] More than half of the respondents (`r ((efsa_00 %>% filter(age>=50) %>% nrow())/(efsa_00 %>% drop_na(age) %>% nrow())*100) %>% round(0)`%) are older than 50 years, `r ((efsa_00 %>% filter(female==0) %>% nrow())/(efsa_00 %>% drop_na(female) %>% nrow())*100) %>% round(0)`% are men and `r ((efsa_00 %>% filter(education %in% c("3 Master","4 Doctorat")) %>% nrow())/(efsa_00 %>% drop_na(education) %>% nrow())*100) %>% round(0)`% have a Master or doctorate degree. `r ((efsa_00 %>% filter(organization.type.short=="1-industry") %>% nrow())/(efsa_00 %>% drop_na(organization.type.short) %>% nrow())*100) %>% round(0)`% of respondents reported working in a company or a trade association, and `r ((efsa_00 %>% filter(organization.type.short=="2-ngo") %>% nrow())/(efsa_00 %>% drop_na(organization.type.short) %>% nrow())*100) %>% round(0)`% in an NGO. The demographic and organizational characteristics of our sample of respondents are summarized in Table 1, and in the supplementary appendix.

Our data also confirms that most of the respondents can be regarded as EFSA stakeholders. `r ((efsa_00 %>% filter(organization.area.food==1) %>% nrow())/(efsa_00 %>% drop_na(organization.area.food) %>% nrow())*100) %>% round(0)`% of respondents identified the policy domain of "food and agriculture" as most relevant to the operations of their organization, `r ((efsa_00 %>% filter(informed.efsa>0) %>% nrow())/(efsa_00 %>% drop_na(informed.efsa) %>% nrow())*100) %>% round(0)`% indicated that they are informed about EFSA's mandate and `r ((efsa_00 %>% filter(affect.decisions.efsa>0) %>% nrow())/(efsa_00 %>% drop_na(affect.decisions.efsa) %>% nrow())*100) %>% round(0)`% reported that EFSA’s decisions may affect the operations of their organization.[^footnote_relation.efsa] Furthermore, `r ((efsa_00 %>% filter(str_detect(interact.efsa,c("2.|3.|4.|5."))==T) %>% nrow())/(efsa_00 %>% drop_na(interact.efsa) %>% nrow())*100) %>% round(0)`% reported that their organization interacts with EFSA at least once a year. Overall, we believe that our respondents represent a relatively diverse sample of external stakeholders of EFSA. 

[^footnote_response.rate]: To estimate response rate, we divided the number of observations by the number of invitations while subtracting the email addresses that returned automatic error messages (*n*=45). However, since some of the respondents received the invitation from other participants rather than directly by us, the exact response rate may be somewhat lower.   

[^footnote_power]: We conducted power calculations through r `pwr` package. Power estimates refer to significance level of 95% in a Two-sample t-test with directional hypothesis.  

[^footnote_relation.efsa]: The last two factors were measured through a -5 to 5 Likert scale. We regarded those who selected a score higher than 0. 

<br>

## *Procedure*
The survey[^footnote_additional_parts] started with a set of pre-manipulation questions about the respondents’ organization, and their perceptions of EU political institutions and several EU agencies. We then asked respondents a set of questions aimed at assessing their prior positions about food safety regulation, and pesticides in particular (relevant to our second hypothesis). To disguise our focus on food policy and pesticides, we framed this section as questions about new technologies, and the opportunities these bring versus the threats they pose. We included in this section questions about technologies related to food, as well as to other policy domains. To even further avoid priming, we then asked the respondents three additional questions regarding the use of machine learning algorithms in decision-making, in line with the abovementioned frame. 

[^footnote_additional_parts]: The survey was also designed to explore the perceptions of stakeholders about EFSA in general (as opposed to the credibility of its regulatory outputs), as well as about several other EU agencies. In this paper, we focus on those parts of the study that are consequential for the examination of our hypotheses. The full survey is available in the supplementary Appendix, and replication materials would be available online. 

We next informed participants that we will present them with a recent case of a regulatory risk assessment on food safety policy, and ask for their opinion about it. The case description included three survey pages: The first page, which was identical for all respondents, included a general background about the regulation of pesticides in the EU. The second page included a short background text about EFSA, and served as the experimental manipulation for its independence from political stakeholders (relevant to our first hypothesis). Participants were randomly assigned to treatment and control conditions. For the treatment group, the text emphasized the independence of EFSA from the EU political institutions and member states. The text of the control condition was designed to be neutral, and stressed instead EFSA’s “advice and communication” roles.

Finally, the third page included a summary of a real EFSA scientific opinion about a specific pesticide. Once more, participants were randomly allocated to one of two pesticide cases from 2015 – one of them was a pesticide approval [*Flupyradifurone*, @european2015conclusion] and the other was a pesticide ban [*Amitrole*, @european2014conclusion]. In accordance with the actual outcome in these cases, in the approved pesticide case, respondents were informed that EFSA could not identify a high risk associated with the use of this pesticide, although EFSA did note it could not completely rule out its risks for human health. In the banned pesticide case, respondents were informed that EFSA identified critical concerns associated with the use of the pesticide. 

The different versions are presented in `r figure.x=figure.x+1`**Figure `r figure.x`**. 

<br>

**Figure `r figure.x`: Experimental conditions (presentation of a risk assessment of a pesticide)**

<br>

After reading the description of EFSA’s risk assessment, respondents were asked about the credibility of EFSA’s opinion (our outcome variable), and next about the degree to which they perceive EFSA, in general, to be independent from political stakeholders (which serves as our observational measure for independence). We then included additional questions about their perceptions of EFSA in general, their familiarity with the agency, frequency of interactions and impact of EFSA decisions on their organization’s operations. We then asked them a set of demographic questions and questions about their professional background. Lastly, we included a comprehension-check, to confirm that respondents have read and understood the regulatory risk assessments.

<br>

## *Variables*

```{r, echo=FALSE, warning=FALSE, message=F}
alpha_considerations = psych::alpha(select(
  efsa_00,
  credibility.pest.q1,
  credibility.pest.q2,
  credibility.pest.q3
))[["total"]][["raw_alpha"]] %>% round(2)

alpha_expertise = psych::alpha(select(efsa_00, credibility.pest.q4,
                                      credibility.pest.q5))[["total"]][["raw_alpha"]] %>% round(2)

library(lavaan)

cfa.model.0 <- ' policy.credibility  =~ credibility.pest.q1 + credibility.pest.q2 + credibility.pest.q3 + credibility.pest.q4 + credibility.pest.q5 + credibility.pest.q6 '

fit0 <- cfa(cfa.model.0,
            std.lv = TRUE,
            missing = "fiml",
            data = efsa_00)

cfa.model.1 <-
  ' non.interference  =~ credibility.pest.q1 + credibility.pest.q2 + credibility.pest.q3
              expert.based =~ credibility.pest.q4 + credibility.pest.q5
              stability   =~ credibility.pest.q6 '

fit1 <- cfa(cfa.model.1, 
           std.lv=TRUE,  
           missing="fiml",  
           data=efsa_00)

anova.1 <- anova(fit1, fit0) %>% tidy()


cfa.model.2 <-
  ' non.interference  =~ credibility.pest.q2 + credibility.pest.q3
              expert.based =~ credibility.pest.q1 + credibility.pest.q4 + credibility.pest.q5
              stability   =~ credibility.pest.q6 '

fit2 <- cfa(cfa.model.2, 
           std.lv=TRUE,  
           missing="fiml",  
           data=efsa_00)

```

Our outcome variable, the *perceived credibility* of the regulatory output, is measured in the survey using six Likert-scale items, ranging between -5 (strongly disagree) and +5 (strongly agree). These items aim to capture the *three aspects or sub-dimensions of policy credibility*, in accordance with our conceptualization: *stability*, *expert-based quality* and *political non-interference*. The first aspect, which regards the time-consistency of the decision, is measured through the following single item: "I believe that EFSA's opinion about the pesticide may change the next time it will be asked to reexamine it" (reversed). The second aspect, which regards the extent to which the decision is based on adequate, professional procedures, is measured through two items: "I believe that the opinion was formed after evaluating all the relevant data and evidence"; "I believe that the assessment of the evidence was based on adequate methods" (Cronbach’s alpha = `r alpha_expertise`, factor scores above 0.8). The third aspect regards the extent to which the regulatory output is essentially impartial/politics-free i.e. whether it is strictly based on relevant considerations without political interference. This aspect is measured through three items: "I believe that the opinion was influenced by political interests" (reversed); "I believe that the opinion was affected by the industry interests" (reversed); "I believe that the opinion was based strictly on scientific considerations" (Cronbach’s alpha = `r alpha_considerations`, factor scores above 0.6). The six items were presented to respondents in a random order, to rule out the possibility that responses to a question are driven by participants’ attempts to assimilate their responses with other questions asked before.[^footnote_cfa]

[^footnote_cfa]: We conducted confirmatory factor analysis using R `lavaan` package. These analyses suggest that the three-factors model fits the data significantly better than a model with a single latent factor for credibility ($\chi^2$ = `r anova.1 %>% filter(term=="fit0") %>% select(Chisq.diff) %>% max() %>% round(1)`, *p*<.001). Fit indices of the two models, and factor loadings are reported in the supplementary appendix, along with the distributions of all items and their correlations. It should be noted that the item "I believe that the opinion was based strictly on scientific considerations", is more strongly correlated with the two items of the expert-based dimension. Still, for theoretical reasons, we believe that this item should be included in the non-interference dimension, to better capture the concept. 

Our *first explanatory variable* is the *perceived independence of EFSA* from political stakeholders. This variable is measured through the following item: “EFSA’s opinions can be influenced by EU political institutions (European Commission, Council, Parliament)”. The item, which was showed to the respondents after the abovementioned credibility questions, had a similar scale of -5 to +5. For the analyses, we reversed this item, so that high values indicate greater independence. To the best of our knowledge, this is the first study to explore directly external stakeholders' perceptions about the agencies' political independence (as opposed to measures of their actual independence). This measure is meaningful, given that regulation literature assumes that credibility depends on stakeholders' *subjective beliefs* about the ability of political stakeholders to intervene in agencies' policy decisions.  

While examining the correlation between the perceived independence of EFSA and perceived regulatory credibility is important for exploring the independence--credibility thesis, this test alone does not enable us to effectively depict causal relations between the two variables, even when controlling for covariates. This is due to the concern of endogeneity. To address this limitation, we included the abovementioned manipulation of EFSA’s independence, which enabled us to supplement our observational analysis with a rigorous experimental test. Specifically, we apply an Instrumental Variable (IV) approach, which enables us to examine the causal effect of perceived independence on policy credibility  [@sovey2011instrumental; for a similar approach in public administration research see: @hvidman2019citizens; @grimmelikhuijsen2015effects]. According to this method, we first assess the causal effect of our manipulation on the perceived independence of EFSA and assess variation in perceived independence that can be attributed to this causal effect. Then, in the second stage, we examine whether the variation induced by the manipulation can be associated with the measured variation in our outcome variable, policy credibility. While IV estimation can be also applied in non-experimental designs, using a random assignment significantly enhances the validity of the instrument, by ensuring that it is exogenous and uncorrelated with the error term of the outcome variable. The validity of the IV analysis rests on satisfying several assumptions, which we discuss in the results section.

Our *second explanatory variable* is constituted by *stakeholders’ prior positions* regarding the risk of pesticides. To account for the latter, we asked participants whether the use of pesticides “mainly brings benefits and opportunities, or rather poses a threat” (between -5 “mainly poses a threat” to +5 “mainly brings benefits”). To test the effect of our second hypothesis – the effect of the congruence between stakeholders’ priors and the policy outcome – we explore the interaction between this explanatory variable and the random assignment to one of the two regulatory outcomes (i.e. ban vs. approve pesticide).

The survey also included additional controls, including respondents’ age, gender, educational background, support for EU political institutions, familiarity and intensity of interactions with EFSA and native language. The experimental groups are fairly balanced with respect to the different types of organizations, as well as to demographics and pre-manipulation variables, as demonstrated in `r table.x=table.x+1`**Table `r table.x`**. Our data also confirms that respondents have read the risk assessments and understood their outcomes. `r ((efsa_00 %>% filter(comprehension.check==1) %>% nrow())/(efsa_00 %>% drop_na(comprehension.check) %>% nrow())*100) %>% round(0)`% of the respondents answered correctly the comprehension-check question, in which they were asked whether the pesticide was approved or banned.[^footnote_comprehension_check] 

Summary statistics and correlation matrix for all variables are available in the supplementary appendix.


[^footnote_comprehension_check]: The comprehension-check scores are fairly similar across the two regulatory decisions, with no statistically significant differences. In robust analyses, reported in the supplementary appendix, we excluded from the analysis the few respondents that did not answer the question correctly.  

<br>

**Table `r table.x`: Balancing table**

<br>



# RESULTS
We begin by descriptively exploring the research variables. Thereafter, we examine the relations between perceived independence and credibility based on our observational and experimental measures. Then, we examine the effect of participants’ prior beliefs about the risk of pesticides, across the different regulatory outcomes (ban vs. approve). 

`r figure.x=figure.x+1`**Figure `r figure.x`** graphically presents the means and distribution of the three credibility components with regard to the two decisions. Overall, participants tend to perceive both opinions as relatively credible, with the exception that the approve-pesticide outcome is not perceived as stable/time-consistent (*Mean* = `r efsa_00_approve.pest%>% summarise(mean(credibility.pest.commitment,na.rm=T))%>%max()%>%round(2)` on a scale of -5 to 5, only `r ((efsa_00_approve.pest %>% filter(credibility.pest.commitment>0) %>% nrow())/(efsa_00_approve.pest %>% drop_na(credibility.pest.commitment) %>% nrow())*100) %>% round(0)`% of the answers were above 0). On average, respondents tend to perceive the ban-pesticide outcome as more credible. The three measures are positively associated to varying degress with questions about EFSA’s credibility in general, as well as with trust in the EU institutions, and perceived familiarity with the agency.

<br>




Our main observed independence variable, perceived independence, has a right-skewed distribution (*Mean* = `r efsa_00.t1%>%summarise(mean(independence.polit.efsa))%>%max()%>%round(2)`, *SD* = `r efsa_00.t1%>%summarise(sd(independence.polit.efsa))%>%max()%>%round(2)`, *Median* = `r efsa_00.t1%>%summarise(median(independence.polit.efsa))%>%max()%>%round(2)`). This entails that despite the high formal independence of EFSA, the majority of stakeholders in our sample tended to state that political stakeholders can affect EFSA’s opinions.  Our second observed independent variable, stakeholders’ prior positions regarding pesticides, has a relatively uniform distribution, with the exception that relatively few stakeholders reported +4 or +5 (i.e. very high support for pesticides) (*Mean* = `r efsa_00%>%summarise(mean(supports.pesticides, na.rm=T))%>%max()%>%round(2)`, *SD* = `r efsa_00%>%summarise(sd(supports.pesticides, na.rm=T))%>%max()%>%round(2)`, *Median* = `r efsa_00%>%summarise(median(supports.pesticides, na.rm=T))%>%max()%>%round(2)`). As anticipated, these prior positions are associated with the distinction between the sectors ($\chi^2$(`r chisq.test(efsa_00$supports.pesticides,efsa_00$organization.type.short)[["parameter"]] %>% max()`) = `r chisq.test(efsa_00$supports.pesticides,efsa_00$organization.type.short)[["statistic"]][["X-squared"]] %>% round(2)`, *p*<.01). Stakeholders from NGOs hold relatively negative beliefs towards the use of pesticides (only `r ((efsa_00 %>% filter(organization.type.short=="2-ngo",supports.pesticides>0) %>% nrow())/(efsa_00 %>% filter(organization.type.short=="2-ngo") %>%  drop_na(supports.pesticides) %>% nrow())*100) %>% round(0)`% of them were above zero), whereas stakeholders affiliated with the food industry tend to hold a relatively positive view (`r ((efsa_00 %>% filter(organization.type.short=="1-industry",supports.pesticides<0) %>% nrow())/(efsa_00 %>% filter(organization.type.short=="1-industry") %>%  drop_na(supports.pesticides) %>% nrow())*100) %>% round(0)`% of them reported below zero). Stakeholders from other organizations were spread along the two sides of the scale. 

We now turn to examine our two research hypotheses. 

<br>

## The effect of perceived independence on perceived credibility
```{r, echo=FALSE,warning=FALSE,message=FALSE}



tmod.considerations.null <- lm(credibility.pest.considerations ~
                                 1,
                               data = efsa_00.t1)


tmod.considerations.1 <- update(tmod.considerations.null, . ~ . +
                                  independence.polit.efsa)
tmod.considerations.2 <- update(
  tmod.considerations.null,
  . ~ . +
    independence.polit.efsa +
    ban.pesticide +
    trust.eu.commission +
    trust.eu.parliament +
    trust.eu.council +
    affect.decisions.efsa +
    informed.efsa
)


tmod.expertise.null <- update(tmod.considerations.null, credibility.pest.expertise ~ . )
tmod.expertise.1 <- update(tmod.considerations.1, credibility.pest.expertise ~ . )
tmod.expertise.2 <- update(tmod.considerations.2, credibility.pest.expertise ~ . )

tmod.commitment.null <- update(tmod.considerations.null, credibility.pest.commitment ~ . )
tmod.commitment.1 <- update(tmod.considerations.1, credibility.pest.commitment ~ . )
tmod.commitment.2 <- update(tmod.considerations.2, credibility.pest.commitment ~ . )

```

```{r,echo=FALSE,warning=FALSE,message=FALSE}

  tmod1.1stage <- lm(independence.polit.efsa~ 
                     treatment+
                     ban.pesticide+
                     trust.eu.commission+
                     trust.eu.parliament+
                     trust.eu.council+
                     affect.decisions.efsa+
                     informed.efsa,
                data=efsa_00.t1)

tmod.rf.considerations <- lm(credibility.pest.considerations~ 
                            treatment+
                            ban.pesticide+
                            trust.eu.commission+
                            trust.eu.parliament+
                            trust.eu.council+
                            affect.decisions.efsa+
                            informed.efsa,
                          data=efsa_00.t1) 

reg_iv.considerations <- ivreg(credibility.pest.considerations~
                              independence.polit.efsa+ 
                              ban.pesticide+
                              trust.eu.commission+
                              trust.eu.parliament+
                              trust.eu.council+
                              affect.decisions.efsa+
              informed.efsa|.-independence.polit.efsa+treatment,data=efsa_00.t1)

tmod.rf.expertise <- update(tmod.rf.considerations, credibility.pest.expertise ~ . ) 



reg_iv.expertise <- update(reg_iv.considerations, credibility.pest.expertise ~ . )

tmod.rf.commitment <- update(tmod.rf.considerations, credibility.pest.commitment ~ . ) 


reg_iv.commitment <- update(reg_iv.considerations, credibility.pest.commitment ~ . )

```

```{r, echo=FALSE,warning=FALSE,message=FALSE}

#Beta cpefficients

efsa_00.t1 <- efsa_00.t1 %>% 
  mutate(credibility.pest.considerations.std = scale(credibility.pest.considerations),
         credibility.pest.expertise.std = scale(credibility.pest.expertise),
         credibility.pest.commitment.std = scale(credibility.pest.commitment),
         independence.polit.efsa.std = scale(independence.polit.efsa))


  efsa_00.t1.long <-  efsa_00.t1 %>% 
  gather("outcome.var","value",c("credibility.pest.commitment.std",
                                 "credibility.pest.expertise.std",
                                 "credibility.pest.considerations.std")) 

models.observational.std <- 
efsa_00.t1.long %>% 
  group_by(outcome.var) %>% 
  do(fit = lm(
  value ~
    independence.polit.efsa.std +
    ban.pesticide +
    trust.eu.commission +
    trust.eu.parliament +
    trust.eu.council +
    affect.decisions.efsa +
    informed.efsa,
  data = .)) %>%
  tidy(fit) %>% 
  filter(term=="independence.polit.efsa.std") %>% 
  mutate(lower = estimate - 1.96*std.error,
         upper = estimate + 1.96*std.error)



tmod1.1stage.std <- lm(independence.polit.efsa.std~ 
                   treatment+
                   ban.pesticide+
                   trust.eu.commission+
                   trust.eu.parliament+
                   trust.eu.council+
                   affect.decisions.efsa+
                   informed.efsa,
                data=efsa_00.t1)

models.rf.std <- 
efsa_00.t1.long %>% 
  group_by(outcome.var) %>% 
  do(fit = lm(
  value ~
    treatment +
    ban.pesticide +
    trust.eu.commission +
    trust.eu.parliament +
    trust.eu.council +
    affect.decisions.efsa +
    informed.efsa,
  data = .)) %>%
  tidy(fit) %>% 
  filter(term=="treatment") 

models.iv.std <- 
efsa_00.t1.long %>% 
  group_by(outcome.var) %>% 
  do(fit = ivreg(value ~
                              independence.polit.efsa.std+ 
                              ban.pesticide+
                              trust.eu.commission+
                              trust.eu.parliament+
                              trust.eu.council+
                              affect.decisions.efsa+
              informed.efsa|.-independence.polit.efsa.std+treatment,data= .)) %>%
  tidy(fit) %>% 
  filter(term=="independence.polit.efsa.std") %>% 
  mutate(term = Recode(term,"'independence.polit.efsa.std' = 'independence.polit.efsa.iv.std'"))

models <- rbind(models.observational.std,
                models.rf.std,
                models.iv.std)

t1 <- models.iv.std %>% 
  data.frame() %>% 
  mutate(lower = estimate - 1.96*std.error,
         upper = estimate + 1.96*std.error)
```


We first examine, observationally, the relations between perceived independence and the three aspects/sub-dimensions of credibility. `r table.x=table.x+1`**Table `r table.x`** reports the results of regression analyses. For each of the three aspects, we first analyze the effect of perceived independence alone, and then control for the outcome manipulation (0 = approve pesticide; 1 = ban pesticide), as well as for covariates.[^footnote_regression.interaction.independence]

The coefficients of perceived independence are positive and significant in all models. The correlations with perceived *expertise-based quality* and *stability* are small to modest (*Beta* = `r models.observational.std %>% data.frame() %>% filter(outcome.var=="credibility.pest.expertise.std") %>% select(estimate) %>% max() %>% round(2)`[`r models.observational.std %>% data.frame() %>% filter(outcome.var=="credibility.pest.expertise.std") %>% select(lower) %>% max() %>% round(2)`,`r models.observational.std %>% data.frame() %>% filter(outcome.var=="credibility.pest.expertise.std") %>% select(upper) %>% max() %>% round(2)`] and `r models.observational.std %>% data.frame() %>% filter(outcome.var=="credibility.pest.commitment.std") %>% select(estimate) %>% max() %>% round(2)`[`r models.observational.std %>% data.frame() %>% filter(outcome.var=="credibility.pest.commitment.std") %>% select(lower) %>% max() %>% round(2)`,`r models.observational.std %>% data.frame() %>% filter(outcome.var=="credibility.pest.commitment.std") %>% select(upper) %>% max() %>% round(2)`], respectively, in Models 2,4). This stands in contrast with  regulation literature’s strong emphasis on the relations between independence and credible commitment of policy stability or time-consistency. The correlation with perceived *political non-interference (impartiality) dimension* can be considerred relatively strong (*Beta* = `r models.observational.std %>% data.frame() %>% filter(outcome.var=="credibility.pest.considerations.std") %>% select(estimate) %>% max() %>% round(2)`[`r models.observational.std %>% data.frame() %>% filter(outcome.var=="credibility.pest.considerations.std") %>% select(lower) %>% max() %>% round(2)`,`r models.observational.std %>% data.frame() %>% filter(outcome.var=="credibility.pest.considerations.std") %>% select(upper) %>% max() %>% round(2)`]). 

[^footnote_regression.interaction.independence]: In other models, not shown here, we also confirmed that there is no significant interaction between perceived independence and the decision manipulation.  

<br>

**Table `r table.x`: Regression analyses for regulatory credibility**


<br>


We now turn to our experimental examination of the effect of perceived independence. To reiterate, we manipulated the perceived independence of EFSA by randomly assigning participants to treatment and control conditions. The treatment group read an introduction about EFSA, emphasizing the agency’s independence from political stakeholders, whereas the control group read another text, emphasizing EFSA’s communication and advice roles (see also Figure 1). We regard this random assignment as an *instrumental variable* -- we estimate the extent to which the credibility of the decisions are influenced by the change in the perceived independence that is caused by the manipulation. Applying an IV analysis requires three assumptions: First, the instrument (i.e. the independence treatment) is exogenous, and uncorrelated with the error term of the outcome variable in the model. That assumption is ensured by the random assignment. Second, the exogenous instrument is sufficiently associated to the endogenous explanatory variable (i.e. perceived independence of EFSA). Indeed, our independence manipulation has a positive and significant effect on the perceived independence of EFSA (*Diff* = `r (mean(efsa_00_treatment$independence.polit.efsa,na.rm = T)-mean(efsa_00_control$independence.polit.efsa,na.rm = T)) %>% round(2)` [`r t.test(independence.polit.efsa~treatment,efsa_00)[["conf.int"]][1] %>% round(2)`,`r t.test(independence.polit.efsa~treatment,efsa_00)[["conf.int"]][2] %>% round(2)`], *t* = `r max(t.test(independence.polit.efsa~treatment,efsa_00)[["statistic"]]) %>% abs() %>% round(2)`, *p*<.01).[^footnote_iv.first.stage] Finally, the instrument is assumed, theoretically, to affect the outcome variable only through its effect on the treatment. We belive that we are capable of making that assumption, since the treatment condition specifically emphasized the independence of EFSA from political stakeholders.               

[^footnote_iv.first.stage]: It should be noted that this correlation is slightly weaker than the recommended standard (*F*>10, or *t*>3.16).  

`r table.x=table.x+1`**Table `r table.x`** presents the results of OLS and 2SLS instrumental variable regression analysis for the three dimensions, controlling for covariates. The first Model shows examines the treatment effect on the endogenous variable, perceived personal relevance (the first stage). Thereafter, we examine the direct causal effect of the treatment (the reduced form) and the IV analysis on the three credibility aspects. 

As shown by the reduced form analyses, *participants assigned to the independence treatment condition reported, on average, higher values for all three dimensions of credibility, yet these differences are statistically significant only in relation to the political non-interference dimension* (*t* = `r tmod.rf.considerations %>% tidy() %>% filter(term=="treatment") %>% select(statistic) %>% max() %>% round(2)`, *p* = `r tmod.rf.considerations %>% tidy() %>% filter(term=="treatment") %>% select(p.value) %>% max() %>% round(2)`). Correspondingly, through IV analysis, *we identify with sufficient confidence only the causal effect of perceived independence on that dimension, and not on perceived stability and expert-based*. Model 7 predicts that a one standard deviation increase in perceived independence *causes* an increase of `r t1 %>% filter(outcome.var == "credibility.pest.considerations.std") %>% select(estimate) %>% max() %>% round(2)` [`r t1 %>% filter(outcome.var == "credibility.pest.considerations.std") %>% select(lower) %>% max() %>% round(2)`- `r t1 %>% filter(outcome.var == "credibility.pest.considerations.std") %>% select(upper) %>% max() %>% round(2)`] standard deviations in the impartiality dimension.   


<br>

**Table `r table.x`: Instrumental Variable regression analyses**



<br>

In `r figure.x=figure.x+1`**Figure `r figure.x`**, we graphically summarize our observational and experimental findings regarding the relations bewteen independence and credibility. It shows the standardized coefficients of our observational and experimental measures of EFSA's perceived idependence on the three credibility aspects, which we exctrated from the above models with controls.   

<br>

**Figure `r figure.x`: Coefficients plot -- the effect of perceived independence on policy credibility**


<br>

## The effect of prior beliefs on perceived credibility

```{r, echo=FALSE,warning=FALSE,message=FALSE}


tmod.considerations.11 <- update(tmod.considerations.2, . ~ . + 
                      supports.pesticides)
tmod.considerations.12 <- update(tmod.considerations.2, . ~ . + 
                      ban.pesticide*supports.pesticides)

tmod.expertise.11 <- update(tmod.expertise.2, . ~ . + 
                      supports.pesticides)
tmod.expertise.12 <- update(tmod.expertise.2, . ~ . + 
                      ban.pesticide*supports.pesticides)

tmod.commitment.11 <- update(tmod.commitment.2, . ~ . + 
                      supports.pesticides)
tmod.commitment.12 <- update(tmod.commitment.2, . ~ . + 
                      ban.pesticide*supports.pesticides)

```


Next, we examine the effect of participants’ prior positions on pesticides on credibility, over and above the effect of perceived independence. `r table.x=table.x+1`**Table `r table.x`** shows the results of multiple regression analyses. For each of the three aspects, we include two regression models. First, we replicate the models from Table 2, while adding participants’ prior support for pesticides. Then, to account for the prior positions' congruence with the specific regulatory outcome, we add the interaction between the outcome manipulation and support for pesticides.  

For all three aspects, the interactions between the prior belief support for pesticides  and the outcome manipulation are negative and significant, while the simple effect of support for pesticide is positive and significant. These results indicate that the more a stakeholder regards pesticides in general as safe, the more she is likely to perceive EFSA’s opinion to approve a pesticide as more credible then an opinion to ban it. Also, the more (less) a stakeholder perceives pesticides as safe, the more (less) she is likely to perceive an approve outcome as credible. The marginal effect of support for pesticides in the ban outcome is negative and insignificant for expert-based and non-interference, and positive and insignificant for stability. To facilitate the interpretation of these results, `r figure.x=figure.x+1`**Figure `r figure.x`** graphically illustrates the predictions of the interaction models. 

In relation to the approve outcome, a one standard deviation increase in support for pesticides, is associated with xx standard deviations in the time-consistency dimension, xx standard deviations in the expertise-based dimension and xx standard deviations in the non-interference dimension dimension. Hence, when EFSA finds a low risk associated with the use of a pesticide, prior beliefs plays an important role in shaping the perceived credibility of this outcome. In particular, in relation to the expertise-based quality dimension, it much more influential than the perceived credibility of the agency (*Beta* = xx compared to xx). 

In additional analyses, reported in the supplementary appendix, we further tested the interaction between the outcome manipulation and the different groups of stakeholders. These analyses similarly show that stakeholders from NGOs, which are mostly critical about the safety of pesticides, tend to perceive an opinion to ban a pesticide as more credible -- in the sense of more impartial and more expert-based -- than an opinion to approve the pesticide.

<br>

**Table `r table.x`: Regression analyses for regulatory credibility**



<br>




**Figure `r figure.x`: Interaction between ban opinion and support for pesticides**



<br>

In sum, our analyses suggest stakeholders’ pre-determined perceptions play an important, *and perhaps even greater role in shaping regulatory credibility*. Over and above the effect of stakeholders’ perceptions about the independence of the agency, participants are more likely to perceive a regulatory outcome as credible, mainly in terms of the its impartiality and expertise-based, inasmuch as it corresponds to their prior positions on the matter. Our findings further indicate that stakeholders supporting pesticides are more likely to accept the credibility of a ban outcome than stakeholders opposing pesticides are likely to accept the credibility of an approve outcome. 

In other models reported in the supplementary appendix, we further exmaine the robustness of our findings in relation to the two hypotheses. In these models, We replicate our analyses, while excluding participants who did not answer correctly the comprehension question and participants who are not familiar with EFSA, and testing alternative specifications for the outcome variables measures. In these analyses, the main findings remain largely intact.[^footnote_robust.1]    

[^footnote_robust.1]: When excluding those who did not pass the comprehension task, the effect of perceived independence on Expert based is smaller and marginally significant (p = .11); When excluding those who are not familiar with EFSA, the interaction between support for pesticide and ban pesticide in relation to stability is smaller and marginally significant (p = .11).

<br>



[@miller2016above; @gilardi_2011; @rimkut_2015; @rimkut_2018]


# REFERENCES



